TacticToe: Learning the Game of Tactics

### 2018-01-28 tactictoe_jv.tex
putting back: increasing TacticToe's knowledge section

Additional constraints such as acyclicity and the fact that there is exactly 
one root node are properties of this graph that are preserved during the 
application of the MCTS algorithm. That is why we call it a tree although this 
we do not specify it in this definition.
\end{definition}

@@

%\subsection{Increasing \tactictoe's knowledge}\label{sec:perfect_exp}
%
%We investigate what are the limits of \tactictoe and what benefits additional 
%knowledge could provide. To this end, we will modify the set of features to 
%include features vectors that should not be known in a regular experiment. We  
%include some vectors from the recorded human proof and perform the proof 
%search 
%after the recording instead of before in all other experiments. This 
%experiment 
%is not fair and should only be compared to 
%experiments in the same settings.
%
%For clarity, we will name the set of feature vectors that can be recorded from 
%the current human proof $\mathbb{H}$ and the set of vectors recorded from 
%previous proofs $\mathbb{P}$ (consistent with previous notation?). We note 
%$\pi_1^1$ the projection on the 
%first component returning the label of a feature vector. And we define the 
%function $T$ that takes a tactic and return the list of its tokens.
%
%We will progressively add bigger and bigger 
%subset of $\mathbb{H}$ to $\mathbb{P}$ and observe the effect on the proof 
%search success rates. 
%
%Here are the list of increasing non-trivial subsets of $\mathbb{H}$ we 
%consider:
%\begin{align*}
%\mathbb{F}_1 &= \lbrace (t,g) \in \mathbb{H}\ |\ t \in \pi_1^1(\mathbb{P})  
%   \rbrace \\
%\mathbb{F}_2 &= \lbrace (t,g) \in \mathbb{H}\ |\ \forall x \in T(t).\ \exists 
%t'\in \pi_1^1(\mathbb{P}).\ x \in T(t') \rbrace\\
%\mathbb{F}_3 &= \lbrace (t,g) \in \mathbb{H}\ |\ \forall x \in T(t).\ \exists 
%t'\in \pi_1^1(\mathbb{P}).\ x \in T(t') \vee x\ \mbox{is a theorem} \rbrace\\
%\mathbb{F}_4 &= \lbrace (t,g) \in \mathbb{H}\ |\ \forall x \in T(t).\ \exists 
%t'\in \pi_1^1(\mathbb{P}).\ x \in T(t') \vee x\ \mbox{is a theorem or a term} 
%\rbrace\\
%\end{align*}
%
%
%$\mathbb{F}_1$ is an approximation of what we could get if we had perfect 
%prediction for those tactics.
%
%
%\begin{table}[h]
%\centering\ra{1.3}
%\small
%\begin{tabular}{lll}
%\toprule
% & Additional features & Solved \\
%\midrule
%$\emptyset$   & none & 119 (43.6\%) \\ %NONEv2
%$\mathbb{F}_1$& tactic prediction & 121 (44.3\%) \\ %AFTERTACv2
%$\mathbb{F}_2$& token recombination  & 137 (50.2\%) \\ %AFTERTOKENv2
%$\mathbb{F}_3$& theorem prediction  & 207 (75.8\%) \\ %AFTERTHMTHMv2
%$\mathbb{F}_4$& term prediction & 223 (81.7\%) \\ %AFTERALLv2
%$\mathbb{H}$  & all & 239 (87.5\%) \\ %AFTERSMALLv2
%% $AFTERv2$       & $\mathfrak{H}$ & 245 (89.7\%)  \\
%\bottomrule
%\end{tabular}
%\caption{\label{tab:featue_param} Effect of augmenting \tactictoe's knowledge 
%with tactics from the proof of the tested theorem.} 
%\end{table}
%\todo{good title for this table Additional features}
%
%And we observe in Table~\ref{tab:featue_param} a 
%slight increase compared to the default \tactictoe. We then included all 
%vectors that contains tactics that can be rebuild from tokens of
%tactics in our database. 
%Our search algorithm proved two proofs less that if it had perfect prediction 
%so it means that our prediction algorithm (policy) is doing a good  job at 
%least in this early settings where proofs are easy. 
%Suprisingly, being able to recombine tokens of tactics from the database is 
%barely sufficient to prove more than half of the theorems in this dataset. The 
%Therefore, additionally including in tactics theorems and terms that did not 
%appear in previous tactics is essential. Creating from scratch other arguments 
%may not help as much. This is why we restricted ourselves to predicting 
%arguments of theorem list type and the term type during tactic synthesis. 
%Finally our proof search algorithm sometimes fails even if it knows all the 
%tactic necessary. The two main reasons are that either a crucial tactic 
%exceeds 
%its timeout or that the human proof is too deep to be rediscovered (more than 
%10 steps long).In all those experiments orthogonalization is performed with 
%radius 20.
%
%\subsubsection{Orthogonalization Abstraction}
%Here, we test the benefit of different kind of tactic abstraction.
%All experiments in this table are using orthogonalization.
%
%\begin{table}[t]
%\centering\ra{1.3}
%\small
%\begin{tabular}{ll}
%\toprule
% Technique & Solved \\
%\midrule
%% holyhammer & 79 \\
%  & 122\\
% Orthogonalization & 129\\
%% ortho + term & 126\\    
% Orthogonalization + Abstraction & 160\\
%% ortho + \metis & 162\\
% %ortho + metis + thmortho & 155\\
% %ortho + metis + stacortho & 160\\
%% ortho + \metis + theorem list & 175\\ 
%\bottomrule
%\end{tabular}
%\caption{\label{tab:cfot_param} 
% Effect of orthogonalization and abstraction}
%\end{table}
%We want to know what the optimal number of predictions for tactics different 
%from \metis since \metis has a special status in our algorithm is handled 
%independently.

>>>>

Additional constraints such as acyclicity and the fact that there is exactly 
one root node are properties of this graph that are preserved during the 
application of the MCTS algorithm. That is why we call it a tree although this 
is not specified in this definition.
\end{definition}

@@

\subsection{Increasing \tactictoe'sknowledge}\label{sec:perfect_exp}

\todo{decide to keep this section or not}

We investigate what are the limits of \tactictoe and what benefits additional 
knowledge could provide. To this end, we will modify the set of features to 
include features vectors that should not be known in a regular experiment. We  
include some vectors from the recorded human proof and perform the proof 
search 
after the recording instead of before in all other experiments. This 
experiment 
is not fair and should only be compared to 
experiments in the same settings.

For clarity, we will name the set of feature vectors that can be recorded from 
the current human proof $\mathbb{H}$ and the set of vectors recorded from 
previous proofs $\mathbb{P}$ (consistent with previous notation?). We note 
$\pi_1^1$ the projection on the 
first component returning the label of a feature vector. And we define the 
function $T$ that takes a tactic and return the list of its tokens.

We will progressively add bigger and bigger 
subset of $\mathbb{H}$ to $\mathbb{P}$ and observe the effect on the proof 
search success rates.

Here are the list of increasing non-trivial subsets of $\mathbb{H}$ we 
consider:
\begin{align*}
\mathbb{F}_1 &= \lbrace (t,g) \in \mathbb{H}\ |\ t \in \pi_1^1(\mathbb{P})  
   \rbrace \\
\mathbb{F}_2 &= \lbrace (t,g) \in \mathbb{H}\ |\ \forall x \in T(t).\ \exists 
t'\in \pi_1^1(\mathbb{P}).\ x \in T(t') \rbrace\\
\mathbb{F}_3 &= \lbrace (t,g) \in \mathbb{H}\ |\ \forall x \in T(t).\ \exists 
t'\in \pi_1^1(\mathbb{P}).\ x \in T(t') \vee x\ \mbox{is a theorem} \rbrace\\
\mathbb{F}_4 &= \lbrace (t,g) \in \mathbb{H}\ |\ \forall x \in T(t).\ \exists 
t'\in \pi_1^1(\mathbb{P}).\ x \in T(t') \vee x\ \mbox{is a theorem or a term} 
\rbrace\\
\end{align*}

$\mathbb{F}_1$ is an approximation of what we could get if we had perfect 
prediction for those tactics.

\begin{table}[h]
\centering\ra{1.3}
\small
\begin{tabular}{lll}
\toprule
 & Additional features & Solved \\
\midrule
$\emptyset$   & none & 119 (43.6\%) \\ %NONEv2
$\mathbb{F}_1$& tactic prediction & 121 (44.3\%) \\ %AFTERTACv2
$\mathbb{F}_2$& token recombination  & 137 (50.2\%) \\ %AFTERTOKENv2
$\mathbb{F}_3$& theorem prediction  & 207 (75.8\%) \\ %AFTERTHMTHMv2
$\mathbb{F}_4$& term prediction & 223 (81.7\%) \\ %AFTERALLv2
$\mathbb{H}$  & all & 239 (87.5\%) \\ %AFTERSMALLv2
% $AFTERv2$       & $\mathfrak{H}$ & 245 (89.7\%)  \\
\bottomrule
\end{tabular}
\caption{\label{tab:featue_param} Effect of augmenting \tactictoe's knowledge 
with tactics from the proof of the tested theorem. The experiments was run with 
a time out of 5sec on an older version of \tactictoe, as can be seen in the low 
success rate of the
default strategy.} 
\end{table}

And we observe in Table~\ref{tab:featue_param} a 
slight increase compared to the default \tactictoe. We then included all 
vectors that contains tactics that can be rebuild from tokens of
tactics in our database. 
Our search algorithm proved two proofs less that if it had perfect prediction 
so it means that our prediction algorithm (policy) is doing a good  job at 
least in this early settings where proofs are easy. 
Suprisingly, being able to recombine tokens of tactics from the database is 
barely sufficient to prove more than half of the theorems in this dataset. The 
Therefore, additionally including in tactics theorems and terms that did not 
appear in previous tactics is essential. Creating from scratch other arguments 
may not help as much. This is why we restricted ourselves to predicting 
arguments of theorem list type and the term type during tactic synthesis. 
Finally our proof search algorithm sometimes fails even if it knows all the 
tactic necessary. The two main reasons are that either a crucial tactic 
exceeds 
its timeout or that the human proof is too deep to be rediscovered (more than 
10 steps long).In all those experiments orthogonalization is performed with 
radius 20.
%
%\subsubsection{Orthogonalization Abstraction}
%Here, we test the benefit of different kind of tactic abstraction.
%All experiments in this table are using orthogonalization.
%
%\begin{table}[t]
%\centering\ra{1.3}
%\small
%\begin{tabular}{ll}
%\toprule
% Technique & Solved \\
%\midrule
%% holyhammer & 79 \\
%  & 122\\
% Orthogonalization & 129\\
%% ortho + term & 126\\    
% Orthogonalization + Abstraction & 160\\
%% ortho + \metis & 162\\
% %ortho + metis + thmortho & 155\\
% %ortho + metis + stacortho & 160\\
%% ortho + \metis + theorem list & 175\\ 
%\bottomrule
%\end{tabular}
%\caption{\label{tab:cfot_param} 
% Effect of orthogonalization and abstraction}
%\end{table}
%We want to know what the optimal number of predictions for tactics different 
%from \metis since \metis has a special status in our algorithm is handled 
%independently.
